---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  cache = TRUE,
  message = FALSE
)
```

# leedsboundaries

<!-- badges: start -->
<!-- badges: end -->

The goal of leedsboundaries is to show different ways of defining the geographic extent of 'Leeds' in a reproducible way.
Leeds is a city and local authority in the North of England, North of Sheffield, South of Newcastle, East of Manchester and West of Hull.

<!-- To reproduce this document you must have a recent version of R and the following packages loaded: -->

```{r, include=FALSE}
library(tidyverse)
library(osmextract)
library(sf)
```


It is most easily defined by its local authority boundaries, which are as follows:

```{r, message=FALSE}
leeds = ukboundaries::leeds
# plot(leeds$geometry)
mapview::mapview(leeds)
```

For the purposes of transport planning and other applications, other definitions are useful.

One way of defining Leeds is everything in ring roads.
This looks roughly as follows:

```{r}
leeds_inner_ring_road_mway = sf::read_sf("ring-roads-inner-mway-manual.geojson")
mapview::mapview(leeds_inner_ring_road_mway)
```

A neater boundary can be obtained by taking the 'concave hull' of major roads in the rough outline shown above:

```{r}
remotes::install_github("itsleeds/osmextract")
library(tidyverse)
sub_area_name = "leeds"
area_name = "west yorkshire"
extra_tags = c("maxspeed", "ref", "bicycle")
area_osm_lines = osmextract::oe_get(place = area_name, extra_tags = extra_tags)
sub_area_bbox = tmaptools::geocode_OSM(q = sub_area_name, as.sf = TRUE)
# sub_area_bbox$bbox
sub_area_osm_lines = area_osm_lines[sub_area_bbox$bbox, ]
sub_area_osm_main = filter(sub_area_osm_lines, str_detect(highway, "pri|sec|trunk|round|motor"))
# mapview::mapview(sub_area_osm_main)
```

```{r}
sub_area_osm_inner = sub_area_osm_main[leeds_inner_ring_road_mway, , op = sf::st_within]
mapview::mapview(sub_area_osm_inner)
```

```{r}
sub_area_concave = concaveman::concaveman(sub_area_osm_inner)
mapview::mapview(sub_area_concave)
```

A simplified version of the previous polygon is as follows:

```{r}
sub_area_simple = rmapshaper::ms_simplify(sub_area_concave, keep = 0.04)
mapview::mapview(sub_area_simple)
```

The resulting file is saved as `sub_area_simple.geojson` in this repo.

```{r, eval=FALSE}
sf::write_sf(sub_area_simple, "sub_area_simple.geojson")
```

```{r, eval=FALSE}

```

There are various ways to break-up cities into divisions, which can be useful for visualisation or increasing responsiveness in software such as abstreet.
There are many ways to divide-up cities, the simplest being to use existing boundaries, that we will try in this case:

```{r}
u = "http://geoportal1-ons.opendata.arcgis.com/datasets/deeb99fdf09949bc8ed4dc95c80da279_4.geojson"
uk_consituencies = sf::read_sf(u)
plot(uk_consituencies$geometry)
# u_constituencies = "https://api.os.uk/downloads/v1/products/BoundaryLine/downloads?area=GB&format=GeoPackage&redirect"
```

Let's filter-out those based near Leeds:

```{r}
leedsc = uk_consituencies[sub_area_concave, ]
plot(sub_area_simple, reset = FALSE)
plot(leedsc$geometry, add = TRUE)
```

There are 5 main areas that have a substantial chunk in Leeds:

```{r}
sub2 = sub_area_simple %>% 
  sf::st_buffer(0.0001)
leedsci = sf::st_intersection(leedsc, sub2)
# mapview::mapview(leedsc) + mapview::mapview(sub2)
mapview::mapview(leedsci)
leedsci$area = sf::st_area(leedsci)
s = quantile(leedsci$area)
# class(s)
# s[2]
leedsci_large = leedsci %>% 
  filter(area > s[2])
leedsci_large$pcon16nm
```

I'll edit them manually, combining Leeds North East and Leeds North West:

```{r}
leeds_central = leedsci_large %>% 
  filter(pcon16nm == "Leeds Central")
# mapview::mapview(leeds_central) + mapview::mapview(sub2)
# sf::write_sf(leeds_central, "leeds_central.geojson")

leeds_east = leedsci_large %>% filter(pcon16nm == "Leeds East")
# mapview::mapview(leeds_east) 

# leeds_east_edited = leedsci_large %>% 
#   mapedit::editFeatures()
# leeds_east_edited = leeds_east_edited$geometry[6]
# leeds_east_edited = sf::st_intersection(leeds_east_edited, sub2)
# sf::write_sf(leeds_east_edited, "leeds_east_edited.geojson")
leeds_east_edited = sf::read_sf("leeds_east_edited.geojson")
mapview::mapview(leeds_east_edited)

# leeds_north_edited = leedsci_large %>%
#   mapedit::editFeatures()
# leeds_north_edited = leeds_north_edited$geometry[6]
# sf::write_sf(leeds_north_edited, "leeds_north_edited.geojson")
leeds_north_edited = sf::read_sf("leeds_north_edited.geojson")
mapview::mapview(leeds_north_edited)

# leeds_west_edited = leedsci_large %>%
#   mapedit::editFeatures()
# leeds_west_edited = leeds_west_edited$geometry[6]
# leeds_west_edited = sf::st_intersection(leeds_west_edited, sub2)
# sf::write_sf(leeds_west_edited, "leeds_west_edited.geojson")
leeds_west_edited = sf::read_sf("leeds_west_edited.geojson")
mapview::mapview(leeds_west_edited)
```

Alltogether, these are:

```{r}
mapview::mapview(leeds_central) +
  mapview::mapview(leeds_east_edited) +
  mapview::mapview(leeds_west_edited) +
  mapview::mapview(leeds_north_edited) 
```



