---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  cache = TRUE,
  message = FALSE
)
```

# leedsboundaries

<!-- badges: start -->
<!-- badges: end -->

The goal of leedsboundaries is to show different ways of defining the geographic extent of 'Leeds' in a reproducible way.
Leeds is a city and local authority in the North of England, North of Sheffield, South of Newcastle, East of Manchester and West of Hull.

<!-- To reproduce this document you must have a recent version of R and the following packages loaded: -->

```{r, include=FALSE}
library(tidyverse)
library(osmextract)
library(sf)
```


It is most easily defined by its local authority boundaries, which are as follows:

```{r, message=FALSE}
leeds = ukboundaries::leeds
# plot(leeds$geometry)
mapview::mapview(leeds)
```

For the purposes of transport planning and other applications, other definitions are useful.

One way of defining Leeds is everything in ring roads.
This looks roughly as follows:

```{r}
leeds_inner_ring_road_mway = sf::read_sf("ring-roads-inner-mway-manual.geojson")
mapview::mapview(leeds_inner_ring_road_mway)
```

A neater boundary can be obtained by taking the 'concave hull' of major roads in the rough outline shown above:

```{r}
remotes::install_github("itsleeds/osmextract")
library(tidyverse)
sub_area_name = "leeds"
area_name = "west yorkshire"
extra_tags = c("maxspeed", "ref", "bicycle")
area_osm_lines = osmextract::oe_get(place = area_name, extra_tags = extra_tags)
sub_area_bbox = tmaptools::geocode_OSM(q = sub_area_name, as.sf = TRUE)
# sub_area_bbox$bbox
sub_area_osm_lines = area_osm_lines[sub_area_bbox$bbox, ]
sub_area_osm_main = filter(sub_area_osm_lines, str_detect(highway, "pri|sec|trunk|round|motor"))
# mapview::mapview(sub_area_osm_main)
```

```{r}
sub_area_osm_inner = sub_area_osm_main[leeds_inner_ring_road_mway, , op = sf::st_within]
mapview::mapview(sub_area_osm_inner)
```

```{r}
sub_area_concave = concaveman::concaveman(sub_area_osm_inner)
mapview::mapview(sub_area_concave)
```

A simplified version of the previous polygon is as follows:

```{r}
sub_area_simple = rmapshaper::ms_simplify(sub_area_concave, keep = 0.04)
mapview::mapview(sub_area_simple)
```

The resulting file is saved as `sub_area_simple.geojson` in this repo.

```{r, eval=FALSE}
sf::write_sf(sub_area_simple, "sub_area_simple.geojson")
```


